---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  echo = FALSE,
  messages = FALSE,
  # results = FALSE,
  warnings = FALSE,
  # include = FALSE,
  comment = "#>"
)
library(tidyverse)
library(janitor)
library(maps)
library(gt)
source("R/cheese.R")
```

# Tidy Tuesday - National Cheese Day

<!-- badges: start -->
<!-- badges: end -->

This week's Tidy Tuesday data set is about cheese! 🧀

Cheese.com has information on over 1,000 cheeses from around the world. This data set includes information on the name, country of origin, texture, and type of milk used for each cheese.

Tidy Tuesday provided two data tables to work with: `cheeses.csv` and `cheese_details.csv`. `janitor::compare_df_cols()` was used to compare the two data sets and determine that `cheese_details.csv` didn't have any additional information that I wanted to use that weren't already present in `cheeses.csv`.

```{r label="read data", include=FALSE}
raw_cheese <- read_csv("cheeses.csv") %>%
  rowid_to_column("row_id")

raw_cheese_details <- read_csv("cheese_details.csv") %>%
  rowid_to_column("row_id")


```

```{r}
compare_df_cols(raw_cheese, raw_cheese_details) %>%
  gt() %>% 
  cols_label(column_name = "Column Name",
             raw_cheese = "cheeses.csv",
             raw_cheese_details = "cheese_details.csv") %>% 
  tab_header(title = md("**Comparing Two Dataframes**")) %>% 
  tab_spanner(label = "Data Source", 
              columns = c(raw_cheese, raw_cheese_details)) %>% 
  as_raw_html()



```


## Cheeses of the World

I wanted to know how many different cheeses were produced in each country, however the country column in the dataset had anywhere from one to eight countries listed. We need to create a dataframe that lists the country and a single country, so cheeses that have multiple countries listed would have multiple rows in the new dataframe. 

```{r cheese production by country}

```


```{r cheese_map}

world_map <- map_data("world") %>%
  mutate(region = if_else(!is.na(subregion) & region == "United Kingdom", subregion, region)) %>%
  mutate(region = case_when(
    region == "USA" ~ "United States",
    region == "UK" ~ "United Kingdom",
    TRUE ~ region
  ))

cheese_map <- world_map %>%
  left_join(cheese_by_country, by = c("region" = "country")) 


# no_match <- cheese_by_country %>%
#   filter(!country %in% world_map$region)

cheese_map_plot <- ggplot(cheese_map, aes(x = long, y = lat, group = group)) +
  geom_polygon(aes(fill = count), color = "white") +
  coord_fixed(1.3) +
  scale_x_continuous(limits = c(-180, 180)) +
  scale_y_continuous(limits = c(-60, 90)) +
  theme_minimal() +
  scale_fill_viridis_c() +
  labs(
    title = "Numbers of Cheese by Country",
    fill = "Cheese Count",
    x = "",
    y = ""
  )


plot(cheese_map_plot)


```



```{r texture}
# get the top ten textures from cheese_texture

top_five_texture <- cheese_texture %>% 
  slice_max(count, n = 5) 

common_texture_string <- str_c(top_five_texture$texture, collapse = ", ")
```

The most common types of descriptors for cheese texture in this data set include `r common_texture_string`. 

```{r texture table}

cheese_texture %>%
  filter(!is.na(texture)) %>%
  mutate(texture = str_to_title(texture)) %>%
  gt() %>% 
  tab_header(title = md("**Most Popular Cheese Descriptions**"),
             subtitle = "Number of times each phrase shows up in the data set") %>% 
  cols_label(texture = "Texture", 
             count = "Number of References")%>% 
  as_raw_html()

```

```{r milk}

cheese_milk %>%
  filter(!is.na(milk)) %>% 
  mutate(milk = str_to_title(milk)) %>%
  gt() %>% 
  tab_header(title = md("**Most Popular Milk Types**"),
             subtitle = "Number of cheeses using each milk.") %>% 
  cols_label(milk = "Milk Type", 
             count = "Number of Cheeses")%>% 
  as_raw_html()


```


